### 2018-08-06 paper/design.tex
edited solution overview

Our goal is to enable private and reliable file exchange between users 
participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file \(f\) 
through \name; they start by sharing some information out-of-band, \eg from 
their smartphones.
More precisely, they exchange metadata on \(f\), encryption keys, and 
\changeAL{routing information that they will use to transfer the
  file's content over \name's network of unreliable nodes.}
\sonja{here comes more of a solution overview and reference to the outline
  figure.}

@@

\sonja{might need different naming, and deciding about predictive and probabilistic}
\begin{description}
\item [Stateless.] There is no mandatory circuit creation, the file transfer can be
  done in a stateless way. 
\item [Predictive.] The choice of nodes included in the onion routing
  layers is based on a predictive model for availability, disseminated
  according to Figure~\cref{fig:outline}, and queried by random peer sampling.
\item [Probabilistic.] Instead of source routes with one node per onion layer, each
  layer consists of a set of nodes and although the source route still
  determines the sequence of layers, the actual node used for the next
  hop of forwarding is selected from the set in an ad-hoc way.
\end{description}

>>>>

Our goal is to enable private and reliable file exchange between users 
participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file \(f\) 
through \name, they start by sharing some information out-of-band, \eg from 
their smartphones.
More precisely, they exchange metadata on \(f\), encryption keys, and
some of
\changeAL{routing information that they will use to transfer the
  file's content over \name's network of unreliable nodes.} Namely,
the recipient provides a \emph{rendezvous point} for the sender to
initiate the file transfer.
\sonja{here comes more of a solution overview and reference to the outline
  figure.}

@@

\sonja{might need different naming, and deciding about predictive and probabilistic}
\begin{description}
\item [Stateless.] There is no mandatory circuit creation, the file transfer can be
  done in a stateless way. 
\item [Predictive.] The choice of nodes included in the onion routing
  layers is based on a predictive model for availability, disseminated
  according to Figure~\cref{fig:outline}, and queried by random peer sampling.
\item [Probabilistic.] Instead of source routes with one node per onion layer, each
  layer consists of a set of nodes and although the source route still
  determines the sequence of layers, the actual node used for the next
  hop of forwarding is selected from the set in an ad-hoc way.
\item[Onion Routing.] Put simply, in onion routing, the sender creates
  a source route and 
  encapsulates the payload and next-hop information in layers (by
  encryption), that are \emph{peeled} (decrypted) one by one along the
  route. By virtue of these layers, the forwarding nodes on the
  route do not know where on the route they are and thus whether they
  have received a packet directly from the sender or some other
  intermediate node. We base our format for layering and peeling on
  Sphinx~\cite{Sphinx}, with some modification to allow for the
  changes above, described in \cref{Sphinxes}.
\end{description}
